Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-13 GWLDCII.tex
thoughts on 3.15 and started rereading

In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams. The main focus of that paper is to enumerate the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of \hlfix{any positroid cell under this association.}{I'd like to mildly rephrase this because it sounds like we know exactly which cells have non-empty pre-image, which isn't quite what we proved.}

@@

In Section~\ref{sec dim} we examine the dimension of positroids associated to Wilson loop diagrams, and show that the dimension is always equal to three times the number of propagators in the diagram (Theorem~\ref{thm dim}).  While this has been proved by Marcott in \hlfix{[ref]}{Did this get published yet?} using geometric methods, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram.

@@

Generally speaking the propagators in a Wilson loop diagram are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator. If we need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$, we write $(p,<_i)$ to indicate that $p$ is directed from edge $i$ to edge $j$, and $(p,<_j)$ for the opposite direction.

@@

\bas{\begin{tikzpicture}[baseline=(current bounding box.east)]
\begin{scope}
	\drawWLDfragment[8]{3}{0.3} % draw arc
	%\drawnumbers % use this to debug
	% highlight region
	%\centerarc[linehighlight](0,0)(\zero + 3.6*\step:\zero + 5.4*\step:\radius)
	% region label
	%\node[align = center] at (\zero + 4.5*\step:\radius*1.3) {\em \footnotesize 0, 1, or 2 vertices \\[3pt]\em \footnotesize in this region};
	% scope to draw props and their labels
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
		%p_r
		\draw[smallpropagator] (\zero+2.5*\step:\radius*1.1) to [bend left = 55] (\zero + 6.7*\step:\radius*1.1); 
		%q
		\draw[smallpropagator] (\zero+2.6*\step:\radius*1.1) to [bend left = 55] (\zero + 5.3*\step:\radius*1.1); 
		%\draw[smallpropagator,light-gray] (\zero+7.5*\step:\radius*1.1) -- (0:\radius*0.25);  
		\node at (\zero + 2.8*\step:\radius*0.8){\footnotesize $p_r$};
		\node at (\zero + 4.7*\step:\radius*.84){\footnotesize $q$};
	\end{scope}
	% draw nodes
	\newnode[left]{1}{i}
	\newnode[below]{2}{a_r}
	\newnode[below]{3}{}
	\newnode[right]{8}{j_m}
	% case label
	\node at (270:\radius*0.1) {\em all vertices of $p_r$ lie between $a_r-1$ and $j_m$};
\end{scope}
\end{tikzpicture} \qquad \qquad \begin{tikzpicture}[baseline=(current bounding box.east)]
\begin{scope}
	\drawWLDfragment[8]{3}{0.3} % draw arc
	%\drawnumbers % use this to debug
	% highlight region
		% scope to draw props and their labels
	\begin{scope}
		\clipcenterarc(0,0)(\startpoint-20:\endpoint+20:\radius)
		%random prop preventing p_s from contributing a_s-1
		\draw[smallpropagator,gray] (\zero+2.3*\step:\radius) -- (\zero + 16.5*\step:\radius) ;
		%p_s
		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 7.5*\step:\radius*1.1); 
		%p_r
		\draw[smallpropagator] (\zero+2.5*\step:\radius*1.1) to [bend left = 70] (\zero + 4.5*\step:\radius*1.1); 
		%q
		\draw[smallpropagator] (\zero+4.55*\step:\radius*1.1) to [bend left = 70] (\zero + 6.7*\step:\radius*1.1); 
		\node at (\zero + 4.5*\step:\radius*0.55){\footnotesize $p_s$};
		\node at (\zero + 3.5*\step:\radius*0.84){\footnotesize $p_r$};
		\node at (\zero + 6.2*\step:\radius*0.85){\footnotesize $q$};
	\end{scope}
	% draw nodes
	\newnode[left]{1}{i}
	\newnode[below]{2}{}
	\newnode[below]{3}{a_s}
	\newnode[below]{4}{a_r}
	\newnode[below]{5}{}
	\newnode[right]{8}{j_m}
	% case label
	\node at (270:\radius*0.1) {\em all vertices of $p_r$ do not lie between $a_r-1$ and $j_m$};
\end{scope} 
\end{tikzpicture} }\eas
\caption{The two cases of the induction step. Note that $I_i(p_s) <_i I_i(p_r)$}\label{fig:awkward induction step}
\end{figure}
Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and \hlfix{$I_i(p_t) <_i I_i(p_r)$}{$I_i(p_t) <_i I_i(p_s)<_i I_i(p_s)$? Or is the implication clear enough not to be mentioned}\note{Nope: we just need $<_i I_i(p_r)$. $I_i(p_t) <_i I_i(p_r)$ certainly isn't obvious and may not be true}. Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step, and hence the proof.\end{proof}

>>>>

In contrast, the first paper in this series focuses on combinatorial and matroidal properties of the Wilson loop diagrams. The main focus of that paper is to enumerate the positroid cells that are associated to Wilson loop diagrams with a fixed number of vertices and propagators, as well as counting the number of Wilson loop diagrams in the pre-image of \hlfix{any positroid cell in the image of this association.}{I'd like to mildly rephrase this because it sounds like we know exactly which cells have non-empty pre-image, which isn't quite what we proved.} \sanote{changed}

@@

In Section~\ref{sec dim} we examine the dimension of positroids associated to Wilson loop diagrams, and show that the dimension is always equal to three times the number of propagators in the diagram (Theorem~\ref{thm dim}).  While this has been proved by Marcott in \cite{WLDdim} using matroidal arguments, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram.

@@

Generally speaking the propagators in a Wilson loop diagram are undirected, so $(i,j)$ and $(j,i)$ represent the same propagator. If we need to impose a direction on a propagator $p = (i,j)$, for example in order to consider the region ``inside'' or ``outside'' of $p$, we write $(p,<_i)$ to indicate that $p$ is directed from edge $i$ to edge $j$, and $(p,<_j)$ for the opposite direction. {\color{violet} Note to consider while reading: Might it be notationally easier and/or clearer to talk about ordering the propagators as clockwise or counter clockwise? If so, are the benefits of this new notation worth the rewriting?}

@@

\bas{\begin{tikzpicture}[baseline=(current bounding box.east)]
	\drawWLDfragment[9]{3}{0.3} % draw arc
	%\centerarc[linehighlight](0,0)(\zero + 3.6*\step:\zero + 5.4*\step:\radius)
	%\node[align = center] at (\zero + 4.5*\step:\radius*1.3) {\em \footnotesize 0, 1, or 2 vertices \\[3pt]\em \footnotesize in this region};
		%p_r
		\draw[smallpropagator] (\zero+2.3*\step:\radius*1.1) to [bend left = 55] (\zero + 6.7*\step:\radius*1.1); 
		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 5.3*\step:\radius*1.1); 
		\node at (\zero + 2.8*\step:\radius*0.8){\footnotesize $p_r$};
		\node at (\zero + 4.7*\step:\radius*.84){\footnotesize $q$};
	\newnode[below]{2}{a_r}
	\newnode[right]{9}{j_m}
	\node at (270:\radius*0.1) {\em all vertices of $p_r$ lie between $a_r-1$ and $j_m$};
\end{tikzpicture} \qquad \qquad \begin{tikzpicture}[baseline=(current bounding box.east)]
	\drawWLDfragment[10]{3}{0.3} % draw arc
		%random prop preventing p_s from contributing a_s-1
		\draw[smallpropagator,gray] (\zero+2.3*\step:\radius) -- (\zero + 16.5*\step:\radius) ;
		%p_s
		\draw[smallpropagator] (\zero+2.4*\step:\radius*1.1) to [bend left = 55] (\zero + 7.5*\step:\radius*1.1); 
		%p_r
		\draw[smallpropagator] (\zero+2.5*\step:\radius*1.1) to [bend left = 90] (\zero + 4.5*\step:\radius*1.1); 
		\draw[smallpropagator] (\zero+4.55*\step:\radius*1.1) to [bend left = 70] (\zero + 6.7*\step:\radius*1.1); 
		\node at (\zero + 4.5*\step:\radius*0.55){\footnotesize $p_s$};
		\node at (\zero + 3.5*\step:\radius*0.84){\footnotesize $p_r$};
		\node at (\zero + 6.2*\step:\radius*0.85){\footnotesize $q$};
	\newnode[below]{3}{a_s}
	\newnode[below]{4}{a_r}
	\newnode[below]{8}{}
	\newnode[right]{9}{j_m}
	\node at (270:\radius*0.1) {\em all vertices of $p_r$ do not lie between $a_r-1$ and $j_m$};
\end{tikzpicture} }\eas
\caption{The two cases of the induction step. Note that $I_i(p_s) <_i I_i(p_r)$}\label{fig:awkward induction step}
Now repeat the argument above with $p_s$ in place of $p_r$: if the other end of $p_s$ lands on an edge between $q$ and $j_m$ then we have $q \in \cP_{m-1}$ as above; if not then there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and \hlfix{$I_i(p_t) <_i I_i(p_r)$}{$I_i(p_t) <_i I_i(p_s)<_i I_i(p_s)$? Or is the implication clear enough not to be mentioned}\note{Nope: we just need $<_i I_i(p_r)$. $I_i(p_t) <_i I_i(p_r)$ certainly isn't obvious and may not be true}. {\color{violet} May not be necessary, but I think highlighted tex follows from "Now repeat the argument...." \begin{enumerate}\item If $V(p_r) \in [a_r-1, j_m]$ (other end closer to $j_m$) then $q$ inside $p_r$ in $a_r-1$ order. \item Else, $V(p_r) \in [i, a_r+1]$ (Maybe $[i-1, a_r +1]$?). (Main point is that other end closer to $i$) Either way,  admissibility implies that $a_s < a_r$ \item Now we repeat. Either  $V(p_s) \in [a_s-1, j_m]$ then $q$ inside $p_s$ in $a_s-1$ order and we are done \item Else, $V(p_s) \in [i, a_s+1]$ (Maybe $[i-1, a_s +1]$?). Either way, admissibility implies that $a_t < a_s$ and we've already established $a_s < a_r$ \end{enumerate} We don't have to include this argument. It may be totally unnecessary. But I want to make certain that I'm not missing anything.}  Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step, and hence the proof.\end{proof}
